\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Peer Review of the Presentation: Sin 17: Failure to Protect Stored Data}
\date{}

\begin{document}

\maketitle

\section*{Overview of Main Ideas Discussed in the Presentation}

\begin{enumerate}
    \item \textbf{Introduction to Stored Data Security}: It defines stored data highlights the consequences of inadequate protection.
    \item \textbf{The CIA Triad}: The presentation reinforces the foundational importance of the CIA (Confidentiality Integrity and Availability) triad.
    \item \textbf{Access Control Mechanisms}:
    \begin{itemize}
        \item Detailed discussion of identification authentication and authorization.
        \item Overview of access control methodologies such as Discretionary Access Control (DAC) Mandatory Access Control (MAC) Role-Based Access Control (RBAC) and Attribute-Based Access Control (ABAC).
    \end{itemize}
    \item \textbf{Data Encryption}: Explanation of common encryption methods like AES RSA and Twofish their applications and why encryption is vital.
    \item \textbf{Human-Related Risks}:
    \begin{itemize}
        \item Social engineering threats such as phishing and insider threats.
        \item Case studies like the Sacramento phishing attack and Tesla insider breach underscore real-world consequences.
    \end{itemize}
    \item \textbf{Practical Guidance}: Do’s and Don’ts for protecting stored data and spotting weak access controls during code reviews.
\end{enumerate}

\section*{Topics Discussed in the Discussion Forum}

The discussion forum raised pertinent questions such as:

\begin{itemize}
    \item Major errors organizations make in protecting stored data.
    \item The impact of implementing the Principle of Least Privilege.
    \item Balancing data security with accessibility.
    \item Legal and financial repercussions of failing to secure personal data.
\end{itemize}

The presenter fostered engagement by posing situational and reflective questions that encourage critical thinking and application of knowledge.

\section*{Critique of the Presentation Slides (30 Points)}

\subsection*{Improvement Over Original (2023) Slides}

These slides have been meticulously updated to provide examples. 

\subsection*{Flow}

The presentation follows a logical structure beginning with foundational concepts before risks examples and mitigation strategies. 

\subsection*{Topic Coverage}

The slides comprehensively cover the topic addressing multiple facets of stored data protection.

\section*{Critique of the Discussion Forum Activity (10 Points)}

\subsection*{Questions/Comments}

The presenter posed a wide range of insightful questions covering technical legal and practical aspects of stored data protection. 

\subsection*{Major Issues}

The selected questions captured the essence of stored data protection addressing risks preventive measures. 

\section*{Critique of the Discussion Forum Interaction (10 Points)}

\subsection*{Engagement}

The presenter actively engaged in discussions providing thoughtful responses encouraging further dialogue. 

\section*{Suggestions}

\begin{enumerate}
    \item Incorporating more visuals to break up slides.
    \item Adding a summary slide with key takeaways.
    \item Encouraging more peer-driven questions in the discussion forum to broaden perspectives.
\end{enumerate}

Overall the effort and quality of the presentation are commendable.

\end{document}