\documentclass{article}
\usepackage{geometry}
\geometry{margin=1in}

\title{Peer Review of Presentation and Discussion}

\date{}

\begin{document}

\maketitle

\section*{Overview of Presentation}

\textbf{``Sin 15: Not Updating Easily,''} covers common challenges in software updates. It explains the need for updates, like fixing bugs, improving security, and enhancing user experience. Key terms, such as ``patch,'' ``service pack,'' and ``rollback,'' are defined.

Main points include:

\begin{itemize}
    \item \textbf{Installing Extra Software:} Warns against adding unrelated programs, like Apple’s QuickTime update suggesting Safari.
    \item \textbf{Access Controls:} Highlights risks when updates run with high permissions.
    \item \textbf{Prompt Fatigue:} Explains how frequent prompts can annoy users.
    \item \textbf{User Notifications:} Stresses keeping users informed to avoid risks with silent updates.
    \item \textbf{Easy Patching:} Emphasizes making updates simple to apply and allowing easy rollbacks.
\end{itemize}

\section*{Review of Discussion Forum Topics}

The forum extended these points, covering prompt fatigue, risks of extra software, and forced reboots. Questions about trust in updates led to sharing experiences and practical advice, making the forum engaging.

\section*{Critique of Presentation Slides (30 Points)}

\subsection*{Improvement Over Previous Slides}
Compared to past versions, this presentation adds more real examples, like the Crowdstrike driver failure and PS3 firmware issues. These examples make the points more relatable.

\subsection*{Flow of Information}
The presentation moves logically from basics to specific issues. Some slides, however, could benefit from fewer words or added visuals to make the points clearer.

\subsection*{Adequacy of Topic Coverage}
The presentation covers main risks for updating software. Simplifying some terms could help reach a broader audience.

\section*{Critique of Discussion Forum Activity (10 Points)}

\subsection*{Adequacy of Questions}
The questions cover core topics, such as extra software, prompt fatigue, and reboots. A few more questions on ways to address these issues would add value.

\subsection*{Coverage of Major Issues}
The questions tackled significant issues, focusing on user consent, security, and usability. Open-ended questions encouraged a full discussion.

\section*{Critique of Discussion Forum Interaction (10 Points)}

\subsection*{Presenter Engagement}
The presenter responded actively, adding examples and clarifications. This interaction kept the discussion lively and showed strong topic knowledge.

\section*{Recommendations}

The discussion forum added depth, allowing participants to explore challenges together.

\textbf{Recommendations:}

\begin{itemize}
    \item \textbf{Simplify Key Sections:} Use bullets or visuals on text-heavy slides for clarity.
    \item \textbf{Expand Countermeasure Focus:} Add examples of practical solutions, like automated testing.
    \item \textbf{Enhance Visuals:} More diagrams or graphics could help make ideas clearer.
\end{itemize}

These improvements would make the presentation and discussion even more effective for future audiences.

\end{document}