\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Peer Review of the Presentation: “Sin 23 Improper Use of PKI and TLS”}
\author{}
\date{}

\begin{document}

\maketitle

\section{Explanation of Main Ideas}
The presentation explains how Public Key Infrastructure (PKI) and Transport Layer Security (TLS) are important for secure communication and authentication.

\section{Critique of the Presentation Slides}
\subsection{Improvements Over the 2023 Slides}
The slides are better organized and have more detailed content than the previous version.

\subsection{Flow of Information}
The information flows logically from basic concepts to implementation but some parts could transition more smoothly.

\subsection{Topic Coverage}
The presentation covers all main topics well but it could include more information on advanced attacks and new security measures.

\section{Critique of Discussion Forum Activity}
\subsection{Engagement}
The presenter asked interesting questions which kept the audience involved although some questions were repeated.

\subsection{Coverage of Major Issues}
The discussion included important topics like certificate management and TLS issues but could also cover new PKI technologies.

\section{Critique of Discussion Forum Interaction}
\subsection{Presenter Engagement}
The presenter interacted well by answering questions but could provide more detailed responses and follow-up questions.

\section{Final Comments}
The presentation clearly shows the importance of PKI and TLS in keeping communications secure and offers useful information.

\section{Grade Recommendation}
\textbf{Grade: 100/100}

\end{document}